\documentclass[a4paper,oneside,12pt]{book}

%----------------------------------------------------------------------------------------
%	README!
%   Welcome. It's worth having a read through this file
%   to set up the broad parameters, such as the name of
%   the degree, the school/department, the type of work
%   (dissertation/Final Year Project/report, etc. as well
%   as your own details.
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	COVER PAGE
%   The cover page is laid out in title/title.tex. You can choose a colour
%   or black and white logo
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	THESIS INFORMATION
%   Put title, author name, supervisor name, degree, type of work, school, department in here
%   It will be used for the title page and for the embedded PDF information
%----------------------------------------------------------------------------------------

\newcommand{\thesistitle}{DNS Abuse Transparency} % Your thesis title, this is used in the title and abstract
\newcommand{\degree}{Computer Science and Business} % Replace with your degree name, this is used in the title page and abstract
\newcommand{\typeofthesis}{dissertation} % dissertation, Final Year Project, report, etc.
\newcommand{\authorname}{Abdelaziz Abushark} % Your name, this is used in the title page and PDF stuff
%% Do not put your Student ID in the document, as TCD will not publish
%% documents that contain both your name and your Student ID.
\newcommand{\supervisor}{ Dr. Stephen Farrell} % replace with the name of your supervisor
%\newcommand{\cosupervisor}{Dr Alex Lee} % replace with the name of your co-supervisor if you have one
\newcommand{\keywords}{this, that, more} % Replace with keywords for your thesis
\newcommand{\school}{\href{https://www.tcd.ie/scss/}{School of Computer Science and Statistics}} % Your school's name and URL, this is used in the title page
%Edited by HS for engineering

%% Comment out the next line if you don't want a department to appear
%\newcommand{\department}{\href{http://researchgroup.university.com}{Department Name}} % Your research group's name and URL, this is used in the title page


%% Language and font encodings
\usepackage[T1]{fontenc} 
\usepackage[utf8]{inputenc}
\usepackage[english]{babel} 
%% Bibliographical stuff
\usepackage[]{cite}
%% Document size
% include showframe as an option if you want to see the boxes
\usepackage[a4paper,top=2.54cm,bottom=2.54cm,left=2.54cm,right=2.54cm,headheight=16pt]{geometry}
\setlength{\marginparwidth}{2cm}
%% Useful packages
\usepackage{amsmath}
\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
\usepackage[pdftex]{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=black]{hyperref}
\usepackage{hyperxmp}
\usepackage{caption} % if no caption, no colon
\usepackage{sfmath} %use sans-serif in the maths sections too
\usepackage[parfill]{parskip}    % Begin paragraphs with an empty line rather than an indent
\usepackage{setspace} % to permit one-and-a-half or double spacing
\usepackage{enumerate} % fancy enumerations like (i) (ii) or (a) (b) and suchlike
\usepackage{booktabs} % To thicken table lines
\usepackage{fancyhdr}
\usepackage{xcolor} % to get TCD colour on headings
\usepackage{colortbl}
\numberwithin{equation}{chapter} %HS edit for (chapter.equation)
\pagestyle{plain} % Embrace simplicity!
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{longtable}
\usepackage[none]{hyphenat}
\usepackage{booktabs}
\usepackage{float}
\usepackage{subcaption}




\definecolor{tcd_blue}{RGB}{5, 105, 185}
%% use [H] to make the pics do not float around. 
%% It's personal taste but...
%% Uncomment the following block if you want your name and ID at the top of
%% (almost) every page.

%\pagestyle{fancy}
%\fancyhf{} % sets both header and footer to nothing
%\renewcommand{\headrulewidth}{0pt}
%\cfoot{\thepage}
%\ifdefined\authorid
%\chead{\it \authorname\ (\authorid)}
%\else
%\chead{\it \authorname}
%\fi
%% End of block

%% It is good practise to make your font sans-serif to improve the accessibility of your document.  Comment out the following line to disable it (but you really should not)
\renewcommand{\familydefault}{\sfdefault} %use the sans-serif font as default

%% If you insist on not using sans-serif (please don't), consider using Palatino instead of the LaTeX standard
%\usepackage{mathpazo} % Use the Palatino font by default if you prefer it to Computer Modern


%% Format Chapter headings appropriately
\usepackage{titlesec}
\titleformat{\chapter}[hang]{\normalfont\huge\bfseries\color{tcd_blue}}{\thechapter}{1cm}{}{}

\title{\thesistitle}
\author{\authorname}


\hypersetup{
   pdftitle=\thesistitle, % Set the PDF's title to your title
   pdfauthor=\authorname, % Set the PDF's author to your name
   pdfkeywords=\keywords, % Set the PDF's keywords to your keywords
   pdfsubject=\degree, % Set the PDF's keywords to your keywords
   pdfinfo={
     pdfsupervisor=\supervisor, % Set the PDF's supervisor to your supervisor
     %pdfcosupervisor=\cosupervisor, % Set the PDF's cosupervisor to your cosupervisor if using
   }
}

\usepackage{natbib} %harvard style 
\frontmatter
\begin{document}
\input{title/title.tex}
\pagenumbering{roman}
\section*{\Huge\textcolor{tcd_blue}{Declaration}}
\vspace{1cm}
I hereby declare that this \typeofthesis\ is entirely my own work and that it has not been submitted as an exercise for a degree at this or any other university.

\vspace{1cm}
I have read and I understand the plagiarism provisions in the General Regulations of the University Calendar for the current year, found at \url{http://www.tcd.ie/calendar}.
\vspace{1cm}

I have completed the Online Tutorial on avoiding plagiarism `Ready Steady Write', located at \url{http://tcd-ie.libguides.com/plagiarism/ready-steady-write}.
\vspace{1cm}

I consent / do not consent to the examiner retaining a copy of the thesis beyond the examining period, should they so wish (EU GDPR May 2018).
\vspace{1cm}

I agree that this thesis will not be publicly available, but will be available to TCD staff and students in the University’s open access institutional repository on the Trinity domain only, subject to Irish Copyright Legislation and Trinity College Library conditions of use and acknowledgement.  \textbf{Please consult with your supervisor on this last item before agreeing, and delete if you do not consent}
\vspace{3cm}

Signed:~\rule{5cm}{0.3pt}\hfill Date:~\rule{5cm}{0.3pt}

\chapter*{Abstract}

This research project explores the vital subject of DNS (Domain Name System) abuse, which is widespread and jeopardises the reliability and security of the Internet. The integrity of DNS operations has become critical due to the growing reliance on the internet for both personal and professional activity. To promote a safer online environment, this project aims to increase transparency within the DNS ecosystem by examining the forms, effects and current mitigating techniques of DNS abuse. DNS abuse poses serious threats to internet security and includes phishing, confusable domains (typosquatting), domain hijacking, botnets, quick flux hosting, and domain generation algorithms (DGA). Every type of abuse puts users at risk by making identity theft, money loss, data breaches, and system intrusions easier, as well as by undermining confidence in online services. The reseach project emphasises how urgent it is to address these problems because new technologies like IoT, cloud computing, and AI have the potential to make them worse.

The methodology used in this study included a thorough examination of the DNS ecosystem, vulnerability identification, and an assessment of the mitigation initiatives that are currently being undertaken by important parties, such as registries and registrars. Surveying DNS infrastructure providers and stakeholders was a major part of the investigation to determine the existing level of transparency in the mitigation of DNS abuse. This involved assessing the usefulness of transparency reports and how well they work to stop DNS abuse.Key findings point to a serious weakness in DNS abuse mitigation initiatives' openness. Although several organisations have taken positive steps towards transparency, there is still a lack of standardisation and fragmentation in the industry as a whole. The report makes a number of suggestions to improve openness, such as creating uniform reporting guidelines, encouraging greater cooperation between DNS stakeholders, and implementing best practices to deal with DNS abuse in an open and transparent manner.

This research project adds to the current conversation on DNS abuse by providing a practical reform plan and a detailed grasp of its complexities. It establishes the foundation for more successful mitigation of DNS abuse by promoting greater transparency, which ultimately results in a more secure and reliable Internet.




\chapter*{Lay Abstract}

The goal of this project is to address DNS abuse to make the Internet safer. If you think of the Internet as a giant library, DNS is the index that lets you locate the specific book you are looking for. However, some people manipulate this index to point you to the incorrect book, one that could endanger you by installing malicious software on your computer, stealing your personal information, or stealing money without your knowledge. We refer to this type of deceit as DNS abuse, and it is a serious issue since it can cause people to lose faith in the internet. In this study, we examine how malicious actors use DNS to cause harm, how it affects regular internet users like you and me, and the measures taken to prevent them. We took particular note of the transparency and candour with which the Internet's operators handled these issues. We can all trust the Internet better if they are transparent about how they solve these problems. 

To gain an understanding of this, we reviewed publications on countermeasures against DNS abuse and spoke with numerous individuals involved in the Internet's index system. We found that there is still a great deal of room for improvement, despite the fact that some people are making an effort to be more transparent about how they are solving the issue. There is no standard approach to solving or discussing the issue, and nobody is in agreement. Our findings imply that, in order for everyone to collaborate more successfully, we need to improve the system. To ensure that everyone is aware of the steps being taken to protect the internet, we should all be able to deal with DNS abuse in a uniform manner and have a conversation about it. Those who maintain the index system for the Internet may make it feel safer for all of us to use it by being more transparent.

This project clarifies the causes, consequences, and significance of communicating openly and clearly about mitigating DNS abuse. We want to contribute to the development of a safe and reliable online environment for all users by offering suggestions on how to improve.



\newpage
\onehalfspacing\raggedright %\raggedright turns off justification and hyphenation

\section*{\Huge\textcolor{tcd_blue}{Acknowledgements}}

In the name of God, the most Gracious, the most Merciful.

First, I would like to thank God. Everything I do is only done with his permission. I sincerely thank everyone who helped me along the way with this thesis. First, I express my sincere gratitude to Dr. Stephen Farrell, my supervisor, whose knowledge, compassion, and tolerance greatly enhanced my graduate experience. From the beginning to the end of my inquiry, your advice was very helpful.

I also would like to express my gratitude to the study participants who enthusiastically engaged with my work and offered valuable insights into the dynamics of DNS abuse.

I must express my sincere gratitude to my family for their unwavering support and unceasing encouragement during my years of education, as well as during the process of conducting research and composing this project. Without them, this achievement would not have been feasible. I am grateful to my parents for their guidance and experience.

Finally, I would like to thank Trinity College Dublin and my lecturers for giving me opportunities over the past four years.
I am appreciative of what they have offered.




\tableofcontents
\listoffigures
\listoftables
\newpage



\mainmatter
% maintaining separate .tex files for each chapter is good practice
\input{introduction/introduction.tex}
\input{background/background.tex}
\input{Research/research.tex}
\input{project/project.tex}
\input{evaluation/evaluation.tex}
\input{conclusion/conclusion.tex}
\input{Findings/findings}


% note that your supervisor may have a strong opinion on the style of referencing you use. Some background is available at https://www.overleaf.com/learn/latex/Bibtex_bibliography_styles
\bibliographystyle{IEEEtran} %Changed to IEEETran by HS
%\bibliographystyle{unsrt}
\nocite{*}
\bibliographystyle{plainnat}
\bibliography{bibs/sample}
\appendix
\renewcommand{\thechapter}{A\arabic{chapter}}
\input{appendix/appendix.tex}


\end{document}